---
title: "linear model from Web"
author: "Amia Little"
date: "Summer 2024"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

# Methods
All variables are numerical, so we use num ~ num helper file for all three parts.


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS 

### Descriptive Results -- scatterplot



```{r}
plot(SIMS~ARM,data=data)
```

This plot shows that as arm strength increases the sims score increases as well. 



### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The correlation between the two variables is 0.6860073 which shows that their is a positive correlation in which ARM increases.

### Inferential   (Build linear model) 

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The P-value for the intercept is 0.000000000000000
The P-value for the slope is


#### Scatterplot with model fit
```{r}
plot(SIMS~ARM,data=data) 
abline(model.1, col='red')
```

#### Predict at target point

```{r}
newdata= data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval = 'pred')
```

The SIMS prediction for ARM=88, is 0.71.
The predicting interval is (-1.73,314)



### Numerical results

```{r} 
df= data.frame(SIMS=data$SIMS,GRIP=data$GRIP,ARM=data$ARM)
cor(df)
```

Correlation matrix shows that sims correlates with grip and arm. 
Also,grip and arm correlate with each other

## Model 2 SIM~GRIP

### Now add in scatterplot


### Numerical results 


### Inferential  (Build model.2) 

  

#### predict model.2 at target point





## Model 3 SIM~ARM+GRIP 

Prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM.

### Numerical results (cor) 

```{r}
df=data.frame(SIMS=data$SIMS,GRIP=data$GRIP, ARM=data$ARM) 
cor(df)
```
Correlation matrix shows that sims correlates with grip and arm. 
Also,grip and arm correlate with each other
`
  
### Inferential  (Build 2-dimentional model.3) 

```{r}
model.3 = lm(SIMS ~ ARM + GRIP, data= data) 
summary.lm(model.3)
```

The P-value for the F-statistic is 0.00000000000000002.
This means the data fits the model 

P-value for the model perimeters intercept= 0.0000000000000002. , coofiicient of ARM=0.00000000150., and coefficient of GRIP= 0.00000499.





#### predict model.3 at target point

prediction interval of SIMS given a value of 94  for GRIP and 88 as for ARM.

```{r}
newdata = data.frame(GRIP=94, ARM=88) 
predSIMS = predict(model.3, newdata, interval = 'pred' ) 
print(predSIMS)
```

The predicted SIMS score for GRIP=94, ARM=88 is 0.150,the interval predictions are (-2.13, 2.43) 



## Comparing nested models ANOVA Test 

### Model.1 vs Model.3

```{r}
model.1 = lm(SIMS ~ ARM, data= data) 
anova(model.1, model.3)
```
 
```{r}
summary.lm(model.1)
```
 
The anova shows that there is a difference in the models, the p-value is 0.000004 
Model 2 SIMS~ARM+GRIP is better than Model 1 SIMS~ARM because the rss in model 2 is 188.


### Model.2 vs Model.3

## Informally compare Model.1 with model.2

